An Efficient Calculus for Generalised Parikh Images of Regular Languages

### 2022-06-20 main.tex
Finish motivating example + fix CI

This relation can be combined with the constraint that $\TransitionCount{a} >
\TransitionCount{b}$ to obtain $2 - 2l_c > 2 l_b' + l_c'$. Combining this
equation with the requirement from $\SomethingCSomething$ that
$\TransitionCount{c} \geq 1$ and $\TransitionCount{c} = l_c + l_c'$ from
$\AcaOrBc$ gives $0 \geq l_b'$, and since we cannot use a transition a negative
number of times $l_b' = 0$, which gives the automaton in
Figure~\ref{fig:example-simplify-2}.

@@

  \begin{figure}[h]
    \begin{minipage}[b]{0.75\linewidth}
    \centering 
      \includegraphics[width=\textwidth]{aca_or_bc_simplified_3}
      \caption{$\AcaOrBc{}$ after further constraint propagation.}\label{fig:example-simplify-3}
    \end{minipage}
    \end{figure}

This will produce a straightforward product since both automata now have the
same shape, where we essentially only need to expand the self-loops of
$\SomethingCSomething$ and reduce its range labels to only capture a:s. Note
that we got this result by only performing linear inequality reasoning on the
automata of the product versus the number of times each transition would be
used.

>>>>

This relation can be combined with the constraint that $\TransitionCount{a} >
\TransitionCount{b}$, that is that there are more instances in the accepted
string of letters a than b, to obtain $2 - 2l_c > 2 l_b' + l_c'$. Combining this
equation with the requirement from $\SomethingCSomething$ that
$\TransitionCount{c} \geq 1$ and $\TransitionCount{c} = l_c + l_c'$ from
$\AcaOrBc$ gives $0 \geq l_b'$, and since we cannot use a transition a negative
number of times $l_b' = 0$, which gives the automaton in
Figure~\ref{fig:example-simplify-2}.

@@

  \begin{figure}[h]
    \centering 
      \includegraphics[width=0.75\linewidth]{aca_or_bc_simplified_3}
      \caption{$\AcaOrBc{}$ after further constraint propagation.}\label{fig:example-simplify-3}
    \end{figure}

This will produce a straightforward product since both automata now have the
same shape, where we essentially only need to expand the self-loops of
$\SomethingCSomething$ and reduce its range labels to only capture a:s, as seen
in Figure~\ref{fig:final-example}. Note that we got this result by only
performing linear inequality reasoning on the automata of the product versus the
number of times each transition would be used.

\begin{figure}[h]
\centering
    \includegraphics[width=0.75\linewidth]{aca_or_bc_times_something_c_something}
    \caption{$\AcaOrBc{} \times \SomethingCSomething{}$ under the constraint
    $\TransitionCount{a} > \TransitionCount{b}$. Note the fresh variables
    introduced for the transitions (for most transitions the same one, since
    they are all linearly dependent).}\label{fig:final-example}
  \end{figure}

  \begin{figure}[h]
\centering
    \includegraphics[width=0.75\linewidth]{original_product}
    \caption{$\AcaOrBc{} \times \SomethingCSomething{}$ as it would have
    appeared if we had computed it from the initial
    automata.}\label{fig:original-product}
  \end{figure}

To obtain the final Parikh image, we need to tie the inequalities for the
transitions of the automata of the product to the new transition counters we
introduced in the product automaton. The only interesting transition is the one
carrying the c, so we will choose that one for illustration. In that case, the
bridging equation is $r_2 = l_c \land r_2 = r_{\Sigma}$ (and for all others
$=1$), which gives the Parikh image $\exists_{r_2} \TransitionCount{a} = 1 \land
\TransitionCount{b} = 0 \land \TransitionCount{c} = r_2 + 1$, and after trivial
existence-elimination using reasoning on lower bounds (e.g. $r_2 \geq 0$) we
arrive at $\TransitionCount{c} \geq 1$. For comparison, the $\AcaOrBc{} \times
\SomethingCSomething{}$ we would have obtained if we had eagerly computed the
product can be seen in Figure~\ref{fig:original-product}. This would have
introduced a significantly more complicated existentially quantified formula.
